Chapter 2 Draft

### 2020-04-25 Rmd/Draft/Draft.Rmd

>>>>

Now I'm going to explorea small subset of networks from Bartomeus 2015 to see how the analysis would be. Now I show graphically the networks with sankey diagrams. In first place the sankey diagram for the metaweb and then 4 panels in 4 different networks for the 16 different sites that were sampled in this project.

*Add individual chunks to add captions, think about combining panels...*

```{r, fig.align="center", echo=FALSE}

library(knitr)

include_graphics("Bee_fun.pdf", error = T)

include_graphics("Bee_fun_x8_1.pdf", error = T)

include_graphics("Bee_fun_x8_2.pdf", error = T)
